Bayesian exponential random graph modelling of KWL Burial network

### 2020-04-10 analysis/paper/paper.Rmd
add sentences to Bayesian section
update the description for prior in Rmd

Bayesian approach to ERGMs is an efficient computational tool for social network analysis because it incorporates prior information about the network effects into the model and offers uncertainty quantification by evaluating the posterior distribution of the parameters associated with the network effects [@Caimo2015; @Nemmers2019]. This provides better estimations for complex social network models with heterogeneous data [@Caimo2017].

@@

ERGM- consider transitivity by taking into account high-order k-triangles. Triangles and higher order cycles

@@

4. nodematch: uniform homophily that refers to the similarity of connected nodes. A statistics that counts the number of edges between nodes sharing the same covariate value or characteristics.

@@

Normal distribution 𝜃 ∼ Nd (𝜇prior , Σprior ) is viewed as a suitable prior model for the model parameters of interests in network analysis [@Caimo2017]. We specified the prior based on normal distribution that assumes a low density and high transitivity network.

@@

>>>>

Bayesian approach to ERGMs is an efficient computational tool for social network analysis because it incorporates prior information about the network effects into the model and offers uncertainty quantification by evaluating the posterior distribution of the parameters associated with the network effects [@Caimo2015; @Nemmers2019]. This provides better estimations for complex social network models with heterogeneous data [@Caimo2017]. For archaeological data, missing data could be a problem leading to misinterpretation, which can be also reduced by using Bayesian modelling that provides average 80% correct prediction for the ties and allow 25% false with a third of data missing [@Koskinen2010].

@@

@@

4. nodematch: uniform homophily between nodes that refers to the similarity of connected nodes. A statistics that counts the number of edges between nodes sharing the same covariate value or characteristics. We use wealth index and age as covariants that reflects the similarity between nodes.

@@

Normal distribution 𝜃 ∼ Nd (𝜇prior , Σprior ) is viewed as a suitable prior model for the model parameters of interests in network analysis if there is no previous observation for a network[@Caimo2017]. Since our original data presents a pattern of dense ties, we specified the prior based on our observation that assumes a high density and high transitivity network.

@@

## Structure Effects
